LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives

### 2025-05-04 paper/paper.tex
paper: revise abstract and conclusion

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
    The increasing volume of information in cultural heritage institutions necessitates effective knowledge management solutions. Knowledge graphs (KGs), particularly those aligned with ontologies like the CIDOC Conceptual Reference Model (CIDOC-CRM), offer a powerful framework for structuring and accessing this data. However, traditional KG construction is labor-intensive. Recent advancements in Large Language Models (LLMs) present an opportunity for automated knowledge extraction. This paper investigates the feasibility and effectiveness of using LLMs for constructing CIDOC-CRM knowledge graphs from museum archives, employing a single-stage in-context learning approach guided by a derived ontology. We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia. The constructed knowledge graphs are evaluated using both intrinsic (ontology conformance) and extrinsic (Knowledge Base Question Answering - KBQA) metrics.

    Evaluation results demonstrate that larger LLMs achieve substantially higher ontology conformance (exceeding 90\%), which is essential for ensuring semantic consistency. KBQA evaluation revealed a notable baseline performance by LLMs without explicit graph context, suggesting inherent knowledge. While graphs by larger models generally yielded higher KBQA scores, the performance difference between ontology-guided and ontology-free generated graphs was found to be marginal. This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the necessity for more sophisticated evaluation benchmarks to comprehensively assess CIDOC-CRM KG generation methods.
\end{abstract}

@@

Our study contributes to the growing field exploring the synergy between LLMs, ontologies, and knowledge graphs within the cultural heritage domain. Our results demonstrate the potential for creating structurally sound and accurate CIDOC-CRM knowledge graphs automatically. However, we still notice much room for improvement in CIDOC-CRM knowledge graph evaluation methods, particularly in areas beyond the metrics measured in this study, such as entity duplication, a case where the same item appears twice in the same graph under different names. Future research could also explore other ontology integration techniques, refine datasets, and evaluate the scalability of these approaches across diverse archives. The overarching aim is to leverage these technologies to enhance cultural heritage data management, accessibility, and research.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
    Museum archives contain vast amounts of cultural heritage information, but accessing, integrating and analyzing this data effectively remains challenging. Knowledge graphs (KGs), particularly those structured according to ontologies such as the CIDOC Conceptual Reference Model (CIDOC-CRM), offer a powerful solution through semantic representation, facilitating complex queries across diverse datasets. However, traditional KG construction is labor-intensive. Recent advancements in Large Language Models (LLMs) present an opportunity for automated knowledge extraction. This paper investigates the feasibility and effectiveness of using LLMs for constructing CIDOC-CRM knowledge graphs from museum archives, employing a single-stage in-context learning approach guided by a derived ontology. We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia. The constructed knowledge graphs are evaluated using both intrinsic (ontology conformance) and extrinsic (Knowledge Base Question Answering - KBQA) metrics.

    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle. While all generated KGs improved KBQA performance over a no-context baseline, the ontology-guided approach showed limited and mixed impact on KBQA accuracy compared to the ontology-free graphs in our setup. This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the need for more sophisticated evaluation benchmarks to assess CIDOC-CRM KG generation methods.
\end{abstract}

@@

Our study contributes to the growing field exploring the synergy between LLMs, ontologies, and knowledge graphs within the cultural heritage domain. Our results demonstrate the potential for creating structurally sound and accurate CIDOC-CRM knowledge graphs automatically. However, we still notice much room for improvement in how we evaluate CIDOC-CRM knowledge graph generation methods, particularly in areas beyond the metrics measured in this study, such as entity duplication - the same item appearing twice in the same graph under different names. Future research could also explore other ontology integration techniques, refine datasets, and evaluate the scalability of these approaches across diverse archives. The overarching aim is to leverage these technologies to enhance cultural heritage data management, accessibility, and research.
